Measurement of a dwarf galaxy rotational velocity from its Lyman-alpha line emission

### 2016-08-08 paper/letter.tex
rewritting the rotation description

\section*{Additional Information}

The rotation model used was based on the one explored by
\cite{GaravitoCamargo2014}. Ly-$\alpha$ photons are propagated
within a spherical and homogeneous cloud of HI gas undergoing solid
body rotation. The sources of Ly-$\alpha$ photons are located in the
center of the sphere of HI gas. Dust is not taking into account in our
simulations since their effect doesn't affect the morphology of the
Ly-$\alpha$. The radiative transfer simulations were done using
Monte Carlo simulations with the code \cite{CLARA}.

In this model rotation increases the width of the line and the flux at
the line center. Furthermore, observers at different line of sights
(LOS) angles with respect to the rotation axis of the galaxy will observe
different morphologies of the line. LOS parallel to the rotation axis
will tend to observe a double peaked line, while an observer with a LOS
perpendicular to the rotation axis will observed a single peaked
broader line.

The idealized multiphase model consists of spherical, cold, dens clumps of neutral hydrogen (and dust) embedded in a hot, ionized medium. The clumps also have a random and an outflowing velocity component which totals the number of parameters describing the model to be $14$. In order to map out this large parameter space, we randomly drew $2500$ sets of parameters within a observationally realistic range (based on the considerations of \cite{Laursen2013ApJ...766..124L}) yielding a large variety of single-, double- and triple-peaked spectra. The full analysis of the the spectral features as well as more details on the radiative transfer are presented in \cite{Gronke2016}.

>>>>

\section*{The Rotation Model}

The rotation model corresponds to the work presented in
\cite{GaravitoCamargo2014}. 
In that model the Ly-$\alpha$ photons are propagated 
within a spherical and homogeneous cloud of HI gas undergoing solid
body rotation.
The sphere is fully characterized by three parameters: the optical
depth $\tau$ measured from the center to the surface, the HI
temperature, $T$, and the velocity at the surface $V_{\rm max}$.  
Photons are emitted at their natural frequency from the center of the
sphere. 
Including the effect of dust only changes the overall line
normalization but not its shape.  
The results we report in the main body of the paper do not include any
dust model.
In the current work, the radiative transfer simulations were done
using Monte Carlo simulations with the code \texttt{CLARA}
\cite{CLARA}.

The main effects of rotation are the following.
First, rotation breaks spherical symmetry of the
static case, making the line's observed morphology dependent on the
angle between the line-of-sight and the rotation axis.

First, the line width increases with rotational velocity.
Second, the intensity at the line's center alto 
In this model rotation increases the width of the line and the flux at
the line center. 
Furthermore, observers at different line of sights
(LOS) angles with respect to the rotation axis of the galaxy will observe
different morphologies of the line. LOS parallel to the rotation axis
will tend to observe a double peaked line, while an observer with a LOS
perpendicular to the rotation axis will observed a single peaked
broader line.

\section*{The Multiphase Model}
The idealized multiphase model consists of spherical, cold, dens
clumps of neutral hydrogen (and dust) embedded in a hot, ionized
medium. The clumps also have a random and an outflowing velocity
component which totals the number of parameters describing the model
to be $14$. In order to map out this large parameter space, we
randomly drew $2500$ sets of parameters within a observationally
realistic range (based on the considerations of
\cite{Laursen2013ApJ...766..124L}) yielding a large variety of
single-, double- and triple-peaked spectra. The full analysis of the
the spectral features as well as more details on the radiative
transfer are presented in \cite{Gronke2016}.
